Model Fitting

### 2018-09-15 contest/model-fitting/model-fitting.Rmd

We will use a multilevel logistic regression framework. This allows us to include fixed effects, which remain the same for each player, as well as include player-level effects. Since players appear multiple times in the data, the observations are not independent and including a player-level effect allows us to account for this dependence. It also provides a way to examine individual player effects and assess, for instance, whether Nadal is more likely to win at Wimbledon after accounting for other variables. We considered the following models:

@@

plot_grid(aces_ranef, winners_ranef, nets_ranef, ue_ranef)
```

>>>>

We will use a multilevel logistic regression framework. This allows us to include fixed effects, which remain the same for each player, as well as include player-level effects. Since players appear multiple times in the data, the observations are not independent and including a player-level effect allows us to account for this dependence. It also provides a way to examine individual player effects and assess, for instance, whether Federer is more likely to win at Wimbledon after accounting for other variables. We considered the following models:

@@

aces_ranef
winners_ranef
nets_ranef
ue_ranef
```
